---
title: "scores"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

p_fpkm_scores <- '/scratch/trcanmed/DE_RNASeq/dataset/Biodiversa_up5/fpkm_lymphoma_scores.tsv.gz'
p_tmm_scores <- '/scratch/trcanmed/DE_RNASeq/dataset/Biodiversa_up5/tmm_lymphoma_scores.tsv.gz'
p_metadata <- '/scratch/trcanmed/RNASeq_biod_metadata/dataset/july2020/selected_metadata_annot_final'

cla <- read.table("/scratch/trcanmed/RNASeq_biod_metadata/local/share/data/stromal_contamination.txt", sep="\t", header=T)
colnames(cla) <- c('sample_id_R', 'CAF', 'Leucocyte', 'Endothelial')
cla <- cla[, c(1,2,3,4)]
fpkm_scores <- read.table(gzfile(p_fpkm_scores), header=TRUE, stringsAsFactors=FALSE, sep="\t", quote="")
tmm_scores <- read.table(gzfile(p_tmm_scores), header=TRUE, stringsAsFactors=FALSE, sep="\t", quote="")
metadata <- read.table(p_metadata, header=TRUE, stringsAsFactors=FALSE, sep="\t", quote="")
fpkm_scores$sample_id_R <- gsub(".2","-2", rownames(fpkm_scores), fixed=TRUE)
tmm_scores$sample_id_R <- gsub(".2","-2", rownames(tmm_scores), fixed=TRUE)
merge_1 <- merge(metadata, fpkm_scores, by="sample_id_R")
merge_2 <- merge(merge_1, tmm_scores, by="sample_id_R")
merge_3 <- merge(merge_2, cla, by="sample_id_R")

score <- 'Leucocyte'

compare <- function(x, y, log, nx, ny, color=NULL) {
  if (log) {
    x <- log10(x)
    y <- log10(y)
  }
  pe <- cor.test(x, y)
  d <- data.frame(x=x, y=y)
  if (!is.null(color)) {
    d$color <- as.factor(color)
    print(ggplot(d, aes(x=x, y=y,color=color)) +geom_point()+theme_bw()
        +xlab(nx)+ylab(ny)+labs(caption=paste0(pe$estimate, ', pval=', pe$p.value)))
  } else {
    print(ggplot(d, aes(x=x, y=y)) +geom_point()+theme_bw()
        +xlab(nx)+ylab(ny)+labs(caption=paste0(pe$estimate, ', pval=', pe$p.value)))
  }
  return(pe)
}
```

## Preliminary checks

Merge ok? `r nrow(merge_2)` need to be same as `r nrow(metadata)` and `r nrow(fpkm_scores)` and `r nrow(tmm_scores)`

Merge ok? `r nrow(merge_3)` need to be same as `r nrow(cla)`

## Leuco scores 

FPKM vs TMM:

```{r fpkm-tmm}
#pe <- cor.test(merge_2[, paste0(score, ".x")], merge_2[, paste0(score, ".y")])
#ggplot(d, aes(x=x, y=y)) +geom_point()+theme_bw()
#        +xlab(nx)+ylab(ny)+labs(caption=paste0(pe$estimate, ', pval=', pe$p.value)))
ft <- compare(merge_2[, paste0(score, ".x")], merge_2[, paste0(score, ".y")], FALSE, 'fpkm', 'tmm',  merge_2[,'batch'])
```

Claudio's scores vs FPKM:
```{r fpkm-cla}
ft <- compare(merge_3[, paste0(score, ".x")], merge_3[, paste0(score)], FALSE, 'fpkm', 'Claudio', merge_3[,'batch'])
```

Claudio's scores vs TMM:
```{r tmm-cla}
ft <- compare(merge_3[, paste0(score, ".y")], merge_3[, paste0(score)], FALSE, 'tmm', 'Claudio', merge_3[,'batch'])
```


## Endo scores

FPKM vs TMM:

```{r fpkm-tmm-e}
score <- 'Endothelial'
ft <- compare(merge_2[, paste0(score, ".x")], merge_2[, paste0(score, ".y")], FALSE, 'fpkm', 'tmm',  merge_2[,'batch'])
```

Claudio's scores vs FPKM:
```{r fpkm-cla-e}
ft <- compare(merge_3[, paste0(score, ".x")], merge_3[, paste0(score)], FALSE, 'fpkm', 'Claudio', merge_3[,'batch'])
```

Claudio's scores vs TMM:
```{r tmm-cla-e}
ft <- compare(merge_3[, paste0(score, ".y")], merge_3[, paste0(score)], FALSE, 'tmm', 'Claudio', merge_3[,'batch'])
```

## CAF scores

FPKM vs TMM:

```{r fpkm-tmm-c}
score <- 'CAF'
ft <- compare(merge_2[, paste0(score, ".x")], merge_2[, paste0(score, ".y")], FALSE, 'fpkm', 'tmm',  merge_2[,'batch'])
```

Claudio's scores vs FPKM:
```{r fpkm-cla-c}
ft <- compare(merge_3[, paste0(score, ".x")], merge_3[, paste0(score)], FALSE, 'fpkm', 'Claudio', merge_3[,'batch'])
```

Claudio's scores vs TMM:
```{r tmm-cla-c}
ft <- compare(merge_3[, paste0(score, ".y")], merge_3[, paste0(score)], FALSE, 'tmm', 'Claudio', merge_3[,'batch'])
```

## Leuco with log
```{r leucolog}
score <- 'Leucocyte'
ft <- compare(merge_3[, paste0(score, ".x")], merge_3[, paste0(score)], TRUE, 'fpkm', 'Claudio', merge_3[,'batch'])
ft <- compare(merge_3[, paste0(score, ".y")], merge_3[, paste0(score)], TRUE, 'tmm', 'Claudio', merge_3[,'batch'])
```

## CAF with log
```{r caflog}
score <- 'CAF'
ft <- compare(merge_3[, paste0(score, ".x")], merge_3[, paste0(score)], TRUE, 'fpkm', 'Claudio', merge_3[,'batch'])
ft <- compare(merge_3[, paste0(score, ".y")], merge_3[, paste0(score)], TRUE, 'tmm', 'Claudio', merge_3[,'batch'])
```

## Endo with log
```{r caflog}
score <- 'Endothelial'
ft <- compare(merge_3[, paste0(score, ".x")], merge_3[, paste0(score)], TRUE, 'fpkm', 'Claudio', merge_3[,'batch'])
ft <- compare(merge_3[, paste0(score, ".y")], merge_3[, paste0(score)], TRUE, 'tmm', 'Claudio', merge_3[,'batch'])
```